Outline

### 2021-09-23 varia/NEE/Response_to_reviewers.Rmd

## Reviewer #1 (Remarks to the Author):

Nature Ecology and Evolution review:
Global Drivers and vulnerabilities of coral reef fish functions

My overall opinion of this manuscript is positive. The global distribution of these fish functions on coral reefs has not been previously assessed, nor has their overlap or vulnerability. There’s clear novelty, broad interest, compelling results, the manuscript is generally well written and well-structured, and the authors use multiple extensive datasets and a wide array of sound laboratory and statistical methods. Therefore, my overall recommendation is that this article will ultimately be publishable in Nature Ecology and Evolution. However, I am recommending a major revision because this manuscript needs to be substantially improved. While there is little to criticize regarding most of the data, methods, and results, the paper is severely lacking in sufficient detail and information. In many instances, not nearly enough information is provided for the reader to fully comprehend what is being presented, and in some instances key data or methods elements are not provided. There are also too many bold and unnecessary statements that are not properly backed up by the given citations. The authors should also check for grammar errors, as I encountered many throughout the paper. Lastly, there are two instances where I believe the methods are not optimal and should be improved (calculating correlations between functions and estimating species’ length infinity). I will go through the paper line by line and provide my comments and suggestions:

*Thank you for your constructive and detailed review. We have now provide more details in methods and supplementary methods. Further, we updated the approach to estimating correlations by applying multivariate models as suggested. We also thoroughly checked for grammar errors and modified the main text substantially. Overall, we incorporated all comments with exception of the suggested approach to estimating species length infinity. We provide more details of the modifications below.*

Line 3: why not just say “Preserving ecosystem functioning is a critical challenge…”
*We now state "Preserving coral reef functioning is a critical challenge of the 21st century."*

@@

Line 10: what is meant here by “diverging,” perhaps a better word choice is needed.
*Changed to "varying"*

Line 20: these first two statements are overly bold and not well-focused. The authors would do better to precisely outline the issues they fill with this research article, and to do succinctly, with concise, information-driven, factual sentences. Have people really been managing coral reef fisheries with a surplus-production model for thousands of years? Even if true, does this information help place your reader in the context of your study? The citation given referencing millennia of production-based management schemes is not an article about historical ecosystem impacts, but a modern, long-term plant biodiversity experiment. The authors should improve these aspects throughout the paper and ensure proper citations are given.
*We have now substantially changed the first paragraph of the introduction to quickly place the reader in the context of coral reef functioning.*

@@

Line 54: this should say coral reefs, not just reefs, since you do not include other types of reefs, e.g., rocky reefs from temperate locations.
*Done.*

A general comment for the entire results section: very few of the actual results are presented - there is little to no information on the analyses used, there are no numbers/data/statistics provided, and the main results are very quickly glossed over. While the format of NEE dictates that much information be provided in the supplementary material, sufficient information must still be given for the reader to understand how you achieved your conclusions. A good example comes on line 126, where the authors state that by “combining vulnerability scores and species contributions,” they demonstrate how fishing and coral loss will impact fish functions, then a figure reference is provided. The reader has no idea how these things were combined or what analyses were done to reach these conclusions. In the paragraph beginning on line 54, when the authors state that fish functions vary substantially, as a reader I am expecting to find out how they vary, which ones covary, which areas of
the world have high or low functions or high or low multifunctionality, yet all that is stated is that herbivory is negatively correlated with phosphorus excretion. So, while the authors state that they demonstrate clear tradeoffs in services and that biomass alone is insufficient, I must take them for the word and rely only on a figure to provide any detail.

*We now wrote a new, seperate results section.
Further, following the recommendation of another reviewer, we now removed this part of analysis entirely. Functional vulnerability is now discussed by combining our results with the known effects of human stressors on fish community structure.*

Paragraph beginning on line 86: no information is given here as to how these contributions were calculated. The reader will have to constantly reference the supplementary methods to understand the results of the paper.
*We now provide more information in the results section.*

Coming back to line 126: no information is provided as to how this analysis was done or what was quantified, and no actual quantitative results are given. As a reader it’s hard to believe that anything has been truly demonstrated when the only information given is a figure.
*This paragraph is now removed entirely because as we removed this part of the analysis as mentioned above.*

Concluding paragraph: I suggest the authors spend some time reflecting about the management implications of this work. Are there certain high or low functioning areas that should be prioritized? If we have limited resources but need to prioritize some functions, or combinations of functions, to preserve, which should they be?
*This paper aims to demonstrate existing trade-offs among functions and what drives them. In order to have applicable management recommendations, we first need to find out how much of a certain function is 'good'. We are currently still lacking understanding of what a healthy reef really looks like in terms of process-based functions. We added the following sentences: "It is necessary to gauge the state of reef ecosystems based on multiple, complementary, process-based functions, yet our comprehension of
process-based functioning of coral reefs or what a “functional” coral reef really means is still in its infancy.
To appropriately manage coral reef functioning with respect to local needs and stressors, future studies should seek to establish functional baselines for global coral reefs.
Until then, our study suggests that coral reef fish functions can be managed by enhancing standing stock biomass, protecting local key species, and promoting a balanced community structure."*

Figure 3: I am a bit confused on how to interpret the x axis. Negative coefficients indicate higher contribution to function while positive indicate higher contribution to biomass? So, Lethrinids contribute highly to biomass but not piscivory? Please try to make this clearer for the reader.

*The x-axis was showing the difference between the contribution to function and the contribution to biomass. This means that higher values indicate that a certain family tends to contribute more than a certain function compared to its biomass. We now removed this figure, because it seemed to be more confusing than informative.*

@@

Methods: something critical has been missed here despite the extensive use of Bayesian mixed effects models in this paper. These data have an important, intrinsic hierarchical structure that has not been accounted for nor mentioned. In these data, transects are nested in sites, which are nested in localities. This needs to be stated upfront for the reader to understand the structure of the data and its implications. Furthermore, some models may need to be adjusted to account for this hierarchy. Observations from the same spatial units are non-independent and likely exhibit some degree of autocorrelation, so the statistical methods must account for this non-independence. Hence, the models used should be adjusted to include varying intercept random effects for site and locality.

*We adapted all models to include random effects for site and locality and we modeled all five functions simultaneously in a multivariate model structure. Further, we now explicitly discuss the hierarchical structure of the uvc dataset at the start of the method section.*

Line 8: when you selected families for which you have data, was there a minimum in terms of the number of species in this family for which you had data? For instance, did you select an entire family even if you only had data on one species within the family?

*To add in supp methods.*

Line 26/27: here I am getting a bit lost. You say you ran “the model” yet no model has been presented. You then say you ran this model for every combination of body sizes and sea surface temperatures, yet as a reader I don’t know anything about body sizes or sea surface temperatures at this point in the methods/data, so it’s impossible for me to gauge what exactly you are doing. Furthermore, there has been no mention of what environmental data were used or where they came from. You mention sea surface temperatures, but not whether these were measured in-situ during fish transects or came from satellite sources or a climate model. For all instances of environmental data in the paper, the source and resolution of these data must be provided.
*The model mentioned here is talking about the bioenergetic model provided in the R package 'fishflux' that estimates fluxes of carbon, nitrogen, and phosphorus. We now reworded this section to clarify. We also added mentions of body size and sea surface temperature in the first section of the methods.*

@@

“Residuals are parameters, not data. There is a tradition, especially in parts of biology, of using residuals from one model as data in another model. For example, a biologist might regress brain size on body size and then use the brain size residuals as data in another model. This procedure is always a mistake. Residuals are not known. They are parameters, variables with unobserved values. Treating them as known values throws away uncertainty. The right way to adjust for body size is to include it in the same model, preferably a model designed in light of an explicit causal model.”

If all parameters are standardized, regression coefficients are equivalent to correlation coefficients. Thus, in the simplest sense, if you wanted to know the correlation strength between, for example, herbivory and phosphate excretion while accounting for the spatial hierarchy of your data and controlling for biomass and SST, you could run a Bayesian mixed effects model of herbivory ~ phosphate + biomass + SST, or phosphate ~ herbivory + biomass + SST (both of which would provide the same correlation strength). However, the most appropriate way to do this analysis is probably to perform a multivariate mixed effects model (like others performed in this paper), with [herbivory, piscivory, phosphate excretion, nitrate excretion, production] ~ biomass + SST, and to extract the correlation coefficients between the functions from this model. This will provide equivalent results to what several sets of mixed effects regressions between each pair of standardized functions would provide,
but in one holistic analysis.

*We agree with the reviewer on both arguments made. We now included random effects of localities and sites. Further, to estimate correlation coefficients we opted for the most elegant option - multivariate mixed-effects models. This enabled us to estimate correlations on the site, locality, and residual level, as is now shown in figure 2. The only obstacle for using multivariate models was that some transects have missing values (false zeros) for herbivory or piscivory. We tackled this issue by including these observations as missing values, essentially handling them as parameters in the model. This is now explained in the methods section as followed:*
*"In the underwater visual transect database, 291 transects (3%) did not contained herbivores and 4467 transects (49%) did not contain piscivores yielding false zeros for herbivory and piscivory, respectively. We considered these zeros as missing values because the absence of the observation of a herbivore or piscivore does not prove the actual absence of herbivores and piscivores. In fact, it is highly unlikely that a coral reef fish community contains no herbivores and piscivores at all. To avoid removing all transects with missing values for herbivory or piscivory (n = 4620) from our database when running multivariate analyses, we imputed the missing values by adding these observations as parameters in the multivariate models."*

@@

Line 76: again, this appears to be a simple linear model with no random effects, and therefore not a mixed effects model. Perhaps I am missing something? In either case, this model should also be a mixed effects model that accounts for the data structure: transects nested in sites nested in localities, otherwise your data could be highly biased by uneven sampling effort between localities and by autocorrelation within localities.
*As stated earlier, we now included random effects.*

Line 82: What were these weakly informative priors? Standard practice is to provide this as part of the model equation/formula to be completely transparent with the model. Secondly, no information has been given as to how the models were evaluated? There must have been some assessment of model quality? Minimally R hat, chain convergence, posterior predictive checks, etc.
*We now provide the priors we used, and specified how we assessed the model quality. Specifically, we checked, the R hat, trace plots, and posterior prediction plots.*

Line 104: I’d encourage the authors to read carefully over their manuscript. This sentence is an example where the phrase is ambiguous and not clear. “To know how often species are contributing more than average” to me means: in how many transects is there a species that dominates the function. However, what the authors mean is for each species, how often does it dominate a function. So, it is a species-by-species analysis and not a transect-level analysis, and this needs to be clear.
*We now modified the wording to: "Finally, we quantified the frequency of dominance per species, i.e. the number of transects in which a species is dominant for a given function divided by the total number of transects in which that species is observed."*

Line 117: It’s unclear to me whether the authors developed their own model based on the scores from Graham et al, or if they used a model already produced by Graham et al.
*We used the scores from Graham et al. to create a new model and used the model to predict the scores for species that are not provided in that paper. Graham et al. only used three families, so we are aware that this is a big extrapolation. Following reviewer's recommendation, we now removed this analysis from the paper.*

Line 120: why are model formulas/equations provided for other Bayesian models but not here?
*This part was removed.*

Line 121: Reference the supplementary figure otherwise the reader has no basis on which to believe there was a good model fit.
*Same*

Line 127-130: this information is passed over very quickly without enough detail. Please expand this section to better explain exactly how this analysis was done and make it clearer for the reader as to how it should be interpreted.
*Same.*

@@

Line 10: Here the authors have extracted max lengths from FishBase and substituted them for length infinity. Max length and length infinity, while similar values, are not interchangeable. Froese & Binohlan (2005) specifically published methods on how to estimate length infinity from FishBase max length and provided the formula to do so on the FishBase downloads page. The authors could easily convert these raw max length values to estimated length infinity values using this approach. The authors should either make this adjustment or specify why this was not done.

Froese, R. and Binohlan, C. (2000), Empirical relationships to estimate asymptotic length, length at first maturity and length at maximum yield per recruit in fishes, with a simple method to evaluate length frequency data. Journal of Fish Biology, 56: 758-773.

*Thank you for the suggestion. This is the only comment that we decided not to include. The paper by Froese and Binohlan is over twenty years old and the data they used does not include reef fishes. Moreover, asymptotic length can vary significantly across locations depending on temperature and other environmental variables. We therefore opted for a method proposed and applied by Renato Morais and colleagues. They standardize asymptotic lenth to maximum length to avoid underestimating growth. In this method, the parameter k, is adapted to kmax in order to represent a realistic growth curve. Doing this may underestimate growth of juvenile fishes, while the potential overestimation of adult fishes would be very minimal. As visual census data often does not accurately record juveniles and we removed small fishes from this specific analysis, we argue that our method minimizes potential bias considering the data available. The risk of using a general conversion factor would be too big as we would estimate a growth equal to zero for a lot of individuals and potentially dramatically underestimate biomass production.*

Line 11: what is this standardized coefficient? Is there a reference?
*We added the definition and reference. "For k, we used a standardized coefficient that describes the potential growth trajectory of an individual if linf were to be equal to its maximum length (i.e., kmax; Morais & Bellwood, 2018)."*

Line 14: Be careful to reword this sentence, you’ve filtered out all other species than the species in your species list, not the other way around.
*We changed it to "We selected the species of our species list"*

Line 15: I am a bit lost here, what is the “length-frequency method” is this also from Morais?
*The length-frequency method is another, arguably unreliable way to estimate growth trajectories, that is used for some of the data provided on fishbase. We opted to only use growth curve parameters that were estimated from otolith data. We clarified this by saying: "We selected the species of our species list and only included the k estimates coming from otolith studies."*

Line 17: again, what temperatures are you referring to? No information has been given about temperature to this point in the manuscript.
*As mentioned above, we now added text on temperature at the start of the methods section.*

Line 18: “additional” otolith data implies that there were otolith date previously referenced in the manuscript. If this is not the case be sure not to confuse the reader.
*We now clarified this by mentioning otolith data in the previous paragraph.*

Line 19: “All fishes” - there is no information given on how many species were collected or how many families these species represented. You should also mention how these fishes were collected – what method and were they euthanized, etc.?
*Since initial submission, this data was published under the form of a data paper. We now added this reference.*

Line 41: Here you state that you fitted Bayesian Hierarchical models, but no information is given about these models? How are they hierarchical? Why are they hierarchical? What likelihood functions were used? What priors were used? This information should be presented for each of the Bayesian models you conduct in the paper.
*We added more details on the model.*

Line 43: It is not clear how many species and individuals actually had otolith data? 496 estimates yes, but how many species?
*"After combining the two data sources, we obtained 496 estimates of kmax for 181 species across varying temperatures."*

Line 52: natural log transformed.
*Done.*

Line 53: what were these priors? Put them with the model formula.
*To do!*

Line 59: Is this value considered high? Low? Medium? It would be good to give some context for the reader.
*It means that most of the variation (independent of size and sst) is explained by phylogeny. This value is thus considered quite high. We now specify this.*

Line 69: Here you say, “for all 100 trees.” Again, you really have to consider the information you have given to the reader at this point. The reader hasn’t heard anything about any phylogenetic trees, but now you are saying you’ve got 100 of them. Why 100? Where did they come from? This information is really the basic necessities that need to presented before you rush into describing the analyses.
*We added a paragraph on the phylogenetic trees.*

Comment for phylogenetic extrapolation: overall I’m quite impressed with the work you’ve done, and I do believe your phylogenetic analyses are properly executed. However, is it possible to perform some form of cross validation to ensure the accuracy of these extrapolations given that you’ve extrapolated a huge number of species? For instance, image that all the hard data you collected came from closely related species and families, this might produce unreliable “out-of-sample” predictions.
*To do.*

Line 110: It could be good to say how many families and how many species per family since you use these data for extrapolation.
*To do.*
Line 123: combined how?
*Essentially by taking a weighted average of nutrient contents across trophic groups where the weights represent the probability of being in a diet group.*

Line 135: The level of detail given here is really insufficient. Where were these individuals caught? What habitat type? As a reader I don’t know what part of the world they came from or whether they were caught in a lagoon or on a reef crest.
*To add.*

Line 153: how did you define what an outlier is?
*To add.*

Line 161: If you used an informative prior you must give the reasoning as to why and to how you chose the prior.
*To add.*

Extended Data Figure 2: it might be easier to read if you put the names of the functions as figure titles.
*We added the function names.*

Extended Data Figure 5: just a small thing, but some figures have capital letters for the panel labels, and some have lower case.
*Fixed.*

@@

Reviewer #2 (Remarks to the Author):

This manuscript offers a summary of how coral reef fish communities affect ecosystem functions across the globe by analyzing a database of reef fish species abundance in reefs around the world. The authors then calculated five ecosystem functions using multiple, complex methodologies and analyze the role of fish community structure (i.e., richness, body size, trophic level, and immaturity) in individual functions. As presented, no one individual aspect of community structure is revealed to explain ecosystem functioning across global reefs, but the authors suggest that the variation among communities and between regions means that there is no clear objective for protecting coral reef function and that there are no global keystone species to target.

Overall, this manuscript needs to be rewritten, line by line, in order to improve its clarity. Sentences are imprecise throughout, which muddies the take home messages of the discussion and confuses the main objectives of the study. This is an impressive piece of work that has used multiple data sources and synthesized them in unique, groundbreaking ways. When a manuscript involves big data like this, the authors absolutely have to be fully precise with their explanations of why things were done in the way they were. This manuscript unfortunately is not there, from both an ecological and methodological standpoint. Clearer gaps in knowledge need to be addressed in the introduction, more precise language on how these gaps will be addressed needs to be added/changed, and the big picture and small scale implications of what we have learned from this global analyses needs to be outlined better.

*Thank you. We have now rewritten the manuscript substantially. We focused on imroving clarity, we added a results section, and provided much more details in the methods.*

@@

One major point of confusion for me was the lack of any attempt to combine the ecosystem functions mentioned into a multifunctionality framework. The authors even specifically state that it is necessary to examine multiple functions at once in order to understand how reefs may be changing with different fish communities (line 154-6). Well, the data exist in this paper for this to happen! Even a simple average geometric mean of multifunctionality could be informative, especially for identifying hotspots in fish-driven reef function.

*We now added estimates of multifunctionality per locality and and biomass based on a geometric mean as suggested. We agree that suh a measure can be infomative, but we argue that multifunctionality should be interpreted with care as this summarizing measure may obscure the trade-offs between individual functions.*

### 2021-09-23 text/main.Rmd
supp methods

---
output:
  word_document:
    fig_caption: yes
    reference_docx: ../text/word_template_science.docx
bibliography: ../text/global_proc.bib
csl: nature.csl
---

@@

**Abstract:**
Preserving coral reef functioning is a critical challenge of the 21st century. However, a lack of quantitative assessments of multiple functions across large spatial scales has hindered local and regional conservation efforts. We integrate empirically-parametrized bioenergetic models and global community surveys to quantify five key functions mediated by coral reef fishes. We show that functions exhibit critical trade-offs driven by varying community structures, such that no community can maximize all functions. Further, functions are locally dominated by few species, but worldwide, the identity of dominant species greatly varies; more than half of the 1,110 species in our dataset are functionally dominant on a local scale. Our results underline the need for a nuanced approach to coral reef conservation that considers multiple functions beyond the effect of standing stock biomass.

@@

Fish community structures drive the observed trade-offs among functions which can be explained by organismal physiology and life-history traits of the individuals inside communities [@Schiettekatte2020; @Schramski2015].
For example, we observed a clear trade-off between P excretion and biomass production which is largely driven by the age and trophic community structure.
Communities dominated by fishes with high trophic levels are charachterized high P excretion rates because predatory fishes have a P-rich diet (@Allgeier2014).
In contrast, biomass production is high in communities dominated by fishes with low trophic levels because herbivores tend to have higher growth rates [@Morais2018].
Moreover, communities dominated by mature fishes have high values of P excretion because growing fishes are more likely to retain P to form P-rich bones [@Schiettekatte2020; @Hood], while communities dominated by immature fishes maximize biomass production.
Furthermore, metabolic theory predicts that small-bodied individuals have higher mass-specific metabolic rates, leading to elevated consumption rates and disproportionate contributions to functions that rely on rapid energetic turnover such as herbivory, piscivory, production, and N excretion [@Barneche2018; @Morais2020glob; @Brandl2019science].

@@

Considering multiple functions sheds light on how human-induced shifts in reef fish community structure may impact coral reef ecosystems (Fig. 5).
Fishing and climate-induced coral loss have caused severe changes in reef fish biomass and community structure [@Darling2017; @Graham2017], and our findings suggest that these changes will have strong effects on ecosystem functioning.
Intensive fishing and associated reductions in biomass of large fishes alters the size, age, and trophic structure of fish communities [@Graham2017].
When accounting for the effect of biomass, these effects can enhance nitrogen excretion and production [e.g. @Morais2020glob], but negatively impact phosphorus excretion, herbivory, and piscivory.
Futher, declines in coral cover related to climate change are often associated with a shift toward herbivores, which may deter algal domination [@Graham2006].
However, herbivores have a minor contribution to P excretion [@Allgeier2014; @Schiettekatte2020], so a shift to herbivore dominance and the subsequent decline of community-level P excretion may change the balance of nutrient cycling on reefs, potentially favoring algal growth [@Burkepile2013].

@@

Overall, we demonstrate that the variability in processes that govern the elemental cycling presents an unrecognized challenge for protecting ecosystem functioning. Management strategies that call for the enhancement of coral reef functioning via an economic mindset (i.e. where higher functioning is better) are not feasible. Instead, conserving coral reef ecosystem functioning will require a more nuanced approach that considers processes that vary beyond the effect of standing stock biomass and are subject to variable, local trade-offs, drivers, and anthropogenic threats.

@@

![Fig. 1: Maps of five key ecosystem functions and multifunction, and their relationships with biomass. Left: Dots indicate localities of field surveys, with dot sizes representing the ranked values of the locality-level predictions of functions, and color scales showing categorical assignments (black = lower 25\%, grey = 25-75\%, color = >75\%). Black circular outlines highlight the five localities with the highest values of each function. Multifunction represents the weighted average of the five standardized functions. Right: The predicted values for functions and multifunction with increasing biomass.  The lines represent the average predicted value and the shaded areas show the 95% credible interval of he predictions.](../output/plots/fig1_multimap.png)

![Fig. 2: Correlations among five functions while accounting for biomass and sea surface temperature. a: Modeled correlation coefficients of residual errors. Dots represent the average and lines represent the 95%CI. b-k: Scatter plots of the mean residual error of the functions to demonstrate the correlations.](../output/plots/fig1_multimap.png)

![Fig. 3.  Effects of ecological community variables on five functions. Dots indicate fixed effect values from Bayesian linear regressions that examine effects of species richness, trophic level, size, and immaturity of fishes. To represent both the median and the spread of trophic level, size, and immaturity across individuals inside a community, we included lower and upper 95% quantile values of these three traits as community variables. All data were log-transformed and standardized to compare across functions and variables (see Table S2 for parameter values on non-standardized data). Dots represent the average effect size estimate, and horizontal lines indicate the 95% credible interval.](../output/plots/fig2_com_slopes.png)

![Fig. 4: Local dominance in species contributions for five ecosystem functions on coral reefs. a: The degree of dominance of communities for each function on the site-level. Colored dots represent the raw values and the black dots and lines display the mean and 95\% credible intervals of the average degree of dominance, respectively. Degrees of dominance range between zero (all species contribute equally) and one (a single species is the sole contributor to a given function). The vertical dashed line shows the average of the degree of dominance of 1,000 randomly simulated communities. b: Bar plot showing the proportion of species that are dominant in at least one site relative to the total number of species. In the case of herbivory and piscivory, the total number of herbivores and piscivores, respectively, is used.  c: Species-specific frequencies of dominance in each function across all sites, ranging from zero (species are never dominant) to one (dominant wherever present). A species is categorized as dominant in a community if its contribution to a function is higher than a scenario in which all species are equal (i.e. one divided by the number of species that contribute to the function).](../output/plots/fig3_contributions.png)

![Fig. 5. Vulnerability of five critical functions to fishing and climate change-induced coral loss. Conceptual scheme showing the potential ways in which fishing and climate change may affect functions through their effects on biomass and community structure.](../output/plots/figure_4_vuln_com.png)

>>>>

---
output:
  word_document:
    fig_caption: yes
    reference_docx: ../text/word_template.docx
bibliography: ../text/global_proc.bib
csl: nature.csl
---

@@

**Abstract:**
Preserving coral reef functioning is a critical challenge of the 21st century. However, a lack of quantitative assessments of multiple functions across large spatial scales has hindered local and regional conservation efforts. We integrate empirically-parametrized bioenergetic models and global community surveys to quantify five key functions mediated by coral reef fishes. We show that functions exhibit critical trade-offs driven by varying community structures, such that no community can maximize all functions. Further, functions are locally dominated by few species, but worldwide, the identity of dominant species greatly varies; more than half of the 1,110 species in our dataset are functionally dominant on a local scale. Our results underline the need for a nuanced, local, and context-dependent approach to coral reef conservation that considers multiple functions beyond the effect of standing stock biomass.

@@

Fish community structures drive the observed trade-offs among functions which can be explained by organismal physiology and life-history traits of the individuals inside communities [@Schiettekatte2020; @Schramski2015].
For example, we observed a clear trade-off between P excretion and biomass production which is largely driven by the age and trophic community structure.
Communities dominated by fishes with high trophic levels are charachterized high P excretion rates because predatory fishes have a P-rich diet (@Allgeier2014).
In contrast, biomass production is high in communities dominated by fishes with low trophic levels because herbivores tend to have higher growth rates [@Morais2018].
Moreover, communities dominated by mature fishes have high values of P excretion because growing fishes are more likely to retain P to form P-rich bones [@Schiettekatte2020; @Hood2005], while communities dominated by immature fishes maximize biomass production.
Furthermore, metabolic theory predicts that small-bodied individuals have higher mass-specific metabolic rates, leading to elevated consumption rates and disproportionate contributions to functions that rely on rapid energetic turnover such as herbivory, piscivory, production, and N excretion [@Barneche2018; @Morais2020glob; @Brandl2019science].

@@

Our global analysis of multiple functions suggests pathways in which human-induced shifts in reef fish community structure may impact coral reef ecosystems (Fig. 5).
Fishing and climate-induced coral loss have caused declines in reef fish biomass and shifts in community structure [@Darling2017; @Graham2017], and our findings suggest that these changes will have effects on ecosystem functioning.
Intensive fishing and associated reductions in biomass of large fishes alters the size, age, and trophic structure of fish communities [@Graham2017].
When accounting for the effect of biomass, these community shifts can enhance nitrogen excretion and production [e.g. @Morais2020glob], but negatively impact phosphorus excretion, herbivory, and piscivory.
Futher, declines in coral cover related to climate change are often associated with a shift toward herbivores, which may deter algal domination [@Graham2006].
Simultaneously, herbivores have a minor contribution to P excretion [@Allgeier2014; @Schiettekatte2020], so a shift to herbivore dominance and the subsequent decline of community-level P excretion may change the balance of nutrient cycling on coral reefs, potentially favoring algal growth in comparison with corals [@Burkepile2013].

@@

Overall, using coral reef fishes, we demonstrate that the variability in processes that govern the elemental cycling presents an unrecognized challenge for protecting ecosystem functioning. Management strategies that call for the enhancement of coral reef functioning via an economic mindset (i.e. where higher functioning is better) are not feasible. Instead, conserving coral reef ecosystem functioning will require a more nuanced approach that considers processes that vary beyond the effect of standing stock biomass and are subject to variable, local trade-offs, drivers, and anthropogenic threats.

@@

Fig. 1: Maps of five key ecosystem functions and multifunction, and their relationships with biomass. Left: Dots indicate localities of field surveys, with dot sizes representing the ranked values of the locality-level predictions of functions, and color scales showing categorical assignments (black = lower 25\%, grey = 25-75\%, color = >75\%). Black circular outlines highlight the five localities with the highest values of each function. Multifunction represents the weighted average of the five standardized functions. Right: The predicted values for functions and multifunction with increasing biomass. The lines represent the average predicted value and the shaded areas show the 95% credible interval of he predictions.

Fig. 2: Correlations among five functions while accounting for biomass and sea surface temperature. a: Modeled correlation coefficients of residual errors. Dots represent the average and lines represent the 95%CI. b-k: Scatter plots of the mean residual error of the functions to demonstrate the correlations.

Fig. 3.  Effects of ecological community variables on five functions. Dots indicate fixed effect values from Bayesian linear regressions that examine effects of species richness, trophic level, size, and immaturity of fishes. To represent both the median and the spread of trophic level, size, and immaturity across individuals inside a community, we included lower and upper 95% quantile values of these three traits as community variables. All data were log-transformed and standardized to compare across functions and variables (see Table S2 for parameter values on non-standardized data). Dots represent the average effect size estimate, and horizontal lines indicate the 95% credible interval. Immaturity is defined as the derivative of the Von Bertalanffy growth model for a given size, and the higher this value, the younger the individual.

Fig. 4: Local dominance in species contributions for five ecosystem functions on coral reefs. a: The degree of dominance of communities for each function on the site-level. Colored dots represent the raw values and the black dots and lines display the mean and 95\% credible intervals of the average degree of dominance, respectively. Degrees of dominance range between zero (all species contribute equally) and one (a single species is the sole contributor to a given function). The vertical dashed line shows the average of the degree of dominance of 1,000 randomly simulated communities. b: Bar plot showing the proportion of species that are dominant in at least one site relative to the total number of species. In the case of herbivory and piscivory, the total number of herbivores and piscivores, respectively, is used.  c: Species-specific frequencies of dominance in each function across all sites, ranging from zero (species are never dominant) to one (dominant wherever present). A species is categorized as dominant in a community if its contribution to a function is higher than a scenario in which all species are equal (i.e. one divided by the number of species that contribute to the function).

Fig. 5. Vulnerability of five critical functions to fishing and climate change-induced coral loss. Conceptual scheme showing the potential ways in which fishing and climate change may affect functions through their effects on biomass and community structure.
